### 2024-10-15 Paper.tex
Update .gitignore and add LaTeX intermediate files and backup files

\documentclass[a4paper,twoside]{article}

\usepackage{epsfig}
\usepackage{subcaption}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{apalike}
\usepackage{algorithm2e}
\usepackage[bottom]{footmisc}
\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.

\begin{document}

\title{[Draft Title] Spatial Temporal Event Spotting in Volleyball Videos}

\author{\authorname{Hoang Quoc Nguyen\sup{1}\orcidAuthor{0000-0000-0000-0000}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
\affiliation{\sup{1}Institute of Problem Solving, XYZ University, My Street, MyTown, MyCountry}
\affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
\email{523503, second\_author\}@kist.re.kr, third\_author@dc.mu.edu}
}

\keywords{The paper must have at least one keyword. The text must be set to 9-point font size and without the use of bold or italic font style. For more than one keyword, please use a comma as a separator. Keywords must be titlecased.}

\abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}

\onecolumn \maketitle \normalsize \setcounter{footnote}{0} \vfill

\section{\uppercase{Introduction}}
\label{sec:introduction}

Your paper will be part of the conference proceedings
therefore we ask that authors follow the guidelines explained in
this example in order to achieve the highest quality possible
\cite{Smith98}.

Be advised that papers in a technically unsuitable form will be
returned for retyping. After returned the manuscript must be
appropriately modified.

\section{\uppercase{Manuscript Preparation}}

We strongly encourage authors to use this document for the
preparation of the camera-ready. Please follow the instructions
closely in order to make the volume look as uniform as possible
\cite{Moore99}.

Please remember that all the papers must be in English and without
orthographic errors.

Do not add any text to the headers (do not set running heads) and
footers, not even page numbers, because text will be added
electronically.

For a best viewing experience the used font must be Times New
Roman, except on special occasions, such as program code
\ref{subsubsec:program_code}.

\subsection{Manuscript Setup}

The template is composed by a set of 7 files, in the
following 2 groups:\\
\noindent {\bf Group 1.} To format your paper you will need to copy
into your working directory, but NOT edit, the following 4 files:
\begin{verbatim}
  - apalike.bst
  - apalike.sty
  - article.cls
  - scitepress.sty
\end{verbatim}

\noindent {\bf Group 2.} Additionally, you may wish to copy and edit
the following 3 example files:
\begin{verbatim}
  - example.bib
  - example.tex
  - scitepress.eps
\end{verbatim}

\subsection{Page Setup}

The paper size must be set to A4 (210x297 mm). The document
margins must be the following:

\begin{itemize}
    \item Top: 3,3 cm;
    \item Bottom: 4,2 cm;
    \item Left: 2,6 cm;
    \item Right: 2,6 cm.
\end{itemize}

It is advisable to keep all the given values because any text or
material outside the aforementioned margins will not be printed.

\subsection{First Section}

This section must be in one column.

\subsubsection{Title and Subtitle}

Use the command \textit{$\backslash$title} and follow the given structure in "example.tex". The title and subtitle must be with initial letters
capitalized (titlecased). The separation between the title and subtitle is done by adding a colon ":" just before the subtitle beginning. In the title or subtitle, words like "is", "or", "then", etc. should not be capitalized unless they are the first word of the title or subtitle. No formulas or special characters of any form or language are allowed in the title or subtitle.

\subsubsection{Authors and Affiliations}

Use the command \textit{$\backslash$author} and follow the given structure in "example.tex". Please note that the name of each author must start with its first name.

\subsubsection{Keywords}

Use the command \textit{$\backslash$keywords} and follow the given structure in "example.tex". Each paper must have at least one keyword. If more than one is specified, please use a comma as a separator. The sentence must end with a period.

\subsubsection{Abstract}

Use the command \textit{$\backslash$abstract} and follow the given structure in "example.tex".
Each paper must have an abstract up to 200 words. The sentence
must end with a period.

\subsection{Second Section}

Files "example.tex" and "example.bib" show how to create a paper
with a corresponding list of references.

This section must be in two columns.

Each column must be 7,5-centimeter wide with a column spacing
of 0,8-centimeter.

The section text must be set to 10-point.

Section, subsection and sub-subsection first paragraph should not
have the first line indent.

To remove the paragraph indentation (only necessary for the
sections), use the command \textit{$\backslash$noindent} before the
paragraph first word.

If you use other style files (.sty) you MUST include them in the
final manuscript zip file.

\subsubsection{Section Titles}

The heading of a section title should be in all-capitals.

Example: \textit{$\backslash$section\{FIRST TITLE\}}

\subsubsection{Subsection Titles}

The heading of a subsection title must be with initial letters
capitalized (titlecased).

Words like "is", "or", "then", etc. should not be capitalized unless
they are the first word of the subsection title.

Example: \textit{$\backslash$subsection\{First Subtitle\}}

\subsubsection{Sub-Subsection Titles}

The heading of a sub subsection title should be with initial letters
capitalized (titlecased).

Words like "is", "or", "then", etc should not be capitalized unless
they are the first word of the sub subsection title.

Example: \textit{$\backslash$subsubsection\{First Subsubtitle\}}

\subsubsection{Tables}

Tables must appear inside the designated margins or they may span
the two columns.

Tables in two columns must be positioned at the top or bottom of the
page within the given margins. To span a table in two columns please add an asterisk (*) to the table \textit{begin} and \textit{end} command.

Example: \textit{$\backslash$begin\{table*\}}

\hspace*{1.5cm}\textit{$\backslash$end\{table*\}}\\

Tables should be centered and should always have a caption
positioned above it. The font size to use is 9-point. No bold or
italic font style should be used.

The final sentence of a caption should end with a period.

\begin{table}[h]
\caption{This caption has one line so it is
centered.}\label{tab:example1} \centering
\begin{tabular}{|c|c|}
  \hline
  Example column 1 & Example column 2 \\
  \hline
  Example text 1 & Example text 2 \\
  \hline
\end{tabular}
\end{table}

\begin{table}[h]
\vspace{-0.2cm}
\caption{This caption has more than one line so it has to be
justified.}\label{tab:example2} \centering
\begin{tabular}{|c|c|}
  \hline
  Example column 1 & Example column 2 \\
  \hline
  Example text 1 & Example text 2 \\
  \hline
\end{tabular}
\end{table}

Please note that the word "Table" is spelled out.

\subsubsection{Figures}

Please produce your figures electronically, and integrate them into
your document and zip file.

Check that in line drawings, lines are not interrupted and have a
constant width. Grids and details within the figures must be clearly
readable and may not be written one on top of the other.

Figure resolution should be at least 300 dpi.

Figures must appear inside the designated margins or they may span
the two columns.

Figures in two columns must be positioned at the top or bottom of
the page within the given margins. To span a figure in two columns please add an asterisk (*) to the figure \textit{begin} and \textit{end} command.

Example: \textit{$\backslash$begin\{figure*\}}

\hspace*{1.5cm}\textit{$\backslash$end\{figure*\}}

Figures should be centered and should always have a caption
positioned under it. The font size to use is 9-point. No bold or
italic font style should be used.

\begin{figure}[!h]
  \centering
   {\epsfig{file = SCITEPRESS.eps, width = 5.5cm}}
  \caption{This caption has one line so it is centered.}
  \label{fig:example1}
 \end{figure}

\begin{figure}[!h]
  \vspace{-0.2cm}
  \centering
   {\epsfig{file = SCITEPRESS.eps, width = 5.5cm}}
  \caption{This caption has more than one line so it has to be justified.}
  \label{fig:example2}
\end{figure}

The final sentence of a caption should end with a period.

Please note that the word "Figure" is spelled out.

\subsubsection{Equations}

Equations should be placed on a separate line, numbered and
centered.\\The numbers accorded to equations should appear in
consecutive order inside each section or within the contribution,
with the number enclosed in brackets and justified to the right,
starting with the number 1.

Example:

\begin{equation}\label{eq1}
    a=b+c
\end{equation}

\subsubsection{Algorithms and Listings}

Algorithms and Listings captions should have font size 9-point, no bold or
italic font style should be used and the final sentence of a caption should end with a period. The separator between the title of algorithms/listings and the name of the algorithm/listing must be a colon.
Captions with one line should be centered and if it has more than one line it should be set to justified.

\begin{algorithm}[!h]
 \caption{How to write algorithms.}
 \KwData{this text}
 \KwResult{how to write algorithm with \LaTeX2e }
 initialization\;
 \While{not at end of this document}{
  read current\;
  \eIf{understand}{
   go to next section\;
   current section becomes this one\;
   }{
   go back to the beginning of current section\;
  }
 }
\end{algorithm}

\bigskip
\subsubsection{Program Code}\label{subsubsec:program_code}

Program listing or program commands in text should be set in
typewriter form such as Courier New.

Example of a Computer Program in Pascal:

\begin{small}
\begin{verbatim}
 Begin
     Writeln('Hello World!!');
 End.
\end{verbatim}
\end{small}

The text must be aligned to the left and in 9-point type.

\subsubsection{Reference Text and Citations}

References and citations should follow the APA (Author, date)
System Convention (see the References section in the compiled
manuscript). As example you may consider the citation
\cite{Smith98}. Besides that, all references should be cited in the
text. No numbers with or without brackets should be used to list the
references.

References should be set to 9-point. Citations should be 10-point
font size.

You may check the structure of "example.bib" before constructing the
references.

For more instructions about the references and citations usage
please see the appropriate link at the conference website.

\section{\uppercase{Copyright Form}}

For the mutual benefit and protection of Authors and
Publishers, it is necessary that Authors provide formal written
Consent to Publish and Transfer of Copyright before publication of
the Book. The signed Consent ensures that the publisher has the
Author's authorization to publish the Contribution.

The copyright form is located on the authors' reserved area.

The form should be completed and signed by one author on
behalf of all the other authors.

\section{\uppercase{Conclusions}}
\label{sec:conclusion}

Please note that ONLY the files required to compile your paper should be submitted. Previous versions or examples MUST be removed from the compilation directory before submission.

We hope you find the information in this template useful in the preparation of your submission.

\section*{\uppercase{Acknowledgements}}

If any, should be placed before the references section
without numbering. To do so please use the following command:
\textit{$\backslash$section*\{ACKNOWLEDGEMENTS\}}

\bibliographystyle{apalike}
{\small
\bibliography{example}}

\section*{\uppercase{Appendix}}

If any, the appendix should appear directly after the
references without numbering, and not on a new page. To do so please use the following command:
\textit{$\backslash$section*\{APPENDIX\}}

\end{document}

### 2024-10-15 Paper.tex
Update author affiliation and keywords in Paper.tex

@@
 
-\author{\authorname{Hoang Quoc Nguyen\sup{1}\orcidAuthor{0000-0000-0000-0000}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
-\affiliation{\sup{1}Institute of Problem Solving, XYZ University, My Street, MyTown, MyCountry}
+\author{\authorname{Hoang Quoc Nguyen\sup{1}\orcidAuthor{0009-0002-2004-9285}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
+\affiliation{\sup{1}Korea Institute of Science and Technology, Seoul, Republic of Korea}
 \affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
@@
 
-\keywords{The paper must have at least one keyword.
-The text must be set to 9-point font size and without the use of bold or italic font style.
-For more than one keyword, please use a comma as a separator.
-Keywords must be titlecased.}
+\keywords{Temporally Precise Spotting, Video Understanding, Spatial Temporal Event Spotting, Volleyball, Sport, Deep Learning}
 
@@
 
-\section{\uppercase{Manuscript Preparation}}
+\section{\uppercase{Related work}}
 
@@
 
-\section{\uppercase{Copyright Form}}
+\section{\uppercase{PROPOSED METHOD}}
 
@@
 
-\section{\uppercase{Conclusions}}
-\label{sec:conclusion}
+\section{\uppercase{EXPERIMENTS}}
+\label{sec:experiments}
+
+Please note that ONLY the files required to compile your paper should be submitted. Previous versions or examples MUST be removed from the compilation directory before submission.
+
+We hope you find the information in this template useful in the preparation of your submission.
+
+\section{\uppercase{CONCLUSIONS}}
+\label{sec:conclusions}
 
@@
 without numbering. To do so please use the following command:
-\textit{$\backslash$section*\{ACKNOWLEDGEMENTS\}}
+
+% \textit{$\backslash$section*\{ACKNOWLEDGEMENTS\}}
 
@@
 references without numbering, and not on a new page. To do so please use the following command:
-\textit{$\backslash$section*\{APPENDIX\}}
+% \textit{$\backslash$section*\{APPENDIX\}}
 

### 2024-10-15 Paper.tex
Update title and abstract in Paper.tex

@@
 
-\title{[Draft Title] Spatial Temporal Event Spotting in Volleyball Videos}
+% \title{Multi-task Architecture for Temporally and Spatially Precise Event Spotting in Volleyball Videos}
+% \title{Dual-Objective Deep Learning Architecture for Accurate Temporal and Spatial Event Detection in Volleyball}
+\title{Multi-Task Temporal and Spatial Networks for High-Precision Event Spotting in Volleyball Videos}
+% \title{Multi-Task Temporal-Spatial Deep Learning for Accurate Event Localization in Volleyball Videos}
+% \title{Multi-Task Deep Framework for Accurate Temporal and Spatial Event Detection in Volleyball Videos}
 
@@
 
-\abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
+% \abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
+\abstract{
+  Accurate event spotting in sports videos relies not only on precise temporal detection but also on spatial understanding of key actions within the frame.
+In volleyball, where fast-paced plays unfold in specific court areas, integrating spatial localization is essential for meaningful analysis.
+We introduce a new task: high-precision spatial-temporal event spotting in volleyball videos, addressing the need to detect both when and where key events occur.
+To tackle this challenge, we develop a novel volleyball event dataset annotated for both temporal and spatial event localization.
+Our proposed multi-task deep learning model leverages this dual focus, jointly predicting event timing and spatial coordinates.
+Remarkably, we find that adding a spatial predictor improves temporal event detection by ???\%, underscoring the synergy between spatial and temporal tasks.
+Evaluations demonstrate state-of-the-art performance on our dataset, surpassing existing methods in mean Average Precision (mAP), and highlighting the benefits of spatial-temporal networks in sports video analysis.
+  }
 

### 2024-10-16 Paper.tex
update

--- 2024-10-15 Paper.tex
@@
 
-\title{[Draft Title] Spatial Temporal Event Spotting in Volleyball Videos}
+% \title{Multi-task Architecture for Temporally and Spatially Precise Event Spotting in Volleyball Videos}
+% \title{Dual-Objective Deep Learning Architecture for Accurate Temporal and Spatial Event Detection in Volleyball}
+\title{MTSN: Multi-Task Temporal and Spatial Network for High-Precision Event Spotting in Volleyball Videos}
+% \title{Multi-Task Temporal-Spatial Deep Learning for Accurate Event Localization in Volleyball Videos}
+% \title{Multi-Task Deep Framework for Accurate Temporal and Spatial Event Detection in Volleyball Videos}
 
@@
 
-\keywords{Temporally Precise Spotting, Video Understanding, Spatial Temporal Event Spotting, Volleyball, Sport, Deep Learning}
+\keywords{Precise Event Spotting, Sports Video Understanding, Spatial Temporal Event Spotting, Deep Learning, Volleyball}
 
-\abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
+% \abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
+\abstract{Precise event spotting is crucial in applications like sports analysis, where both temporal and spatial accuracy are key, especially in fast-paced sports like volleyball.
+We introduce a new task: high-precision spatial-temporal event spotting in volleyball videos, requiring detection of both when and where events occur.
+To address this, we develop a novel volleyball dataset annotated for temporal and spatial event localization and propose a multi-task deep learning model that jointly predicts event timing and spatial coordinates.
+Adding spatial prediction improves temporal event detection by ???\%, demonstrating the synergy between these tasks.
+To the best of our knowledge, this is the first work tackling this task, establishing a strong baseline and providing a foundation for future research in spatial-temporal event spotting.}
 

### 2024-10-16 Paper.tex
Update title and abstract in Paper.tex

--- 2024-10-15 Paper.tex
@@
 
-\title{[Draft Title] Spatial Temporal Event Spotting in Volleyball Videos}
+% \title{Multi-task Architecture for Temporally and Spatially Precise Event Spotting in Volleyball Videos}
+% \title{Dual-Objective Deep Learning Architecture for Accurate Temporal and Spatial Event Detection in Volleyball}
+\title{Multi-Task Temporal and Spatial Networks for High-Precision Event Spotting in Volleyball Videos}
+% \title{Multi-Task Temporal-Spatial Deep Learning for Accurate Event Localization in Volleyball Videos}
+% \title{Multi-Task Deep Framework for Accurate Temporal and Spatial Event Detection in Volleyball Videos}
 
-\author{\authorname{Hoang Quoc Nguyen\sup{1}\orcidAuthor{0009-0002-2004-9285}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
+\author{\authorname{Hoang Quoc Nguyen\sup{1}\sup{2}\orcidAuthor{0009-0002-2004-9285}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
 \affiliation{\sup{1}Korea Institute of Science and Technology, Seoul, Republic of Korea}
-\affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
+\affiliation{\sup{2}University of Science and Technology, Daejeon, Republic of Korea}
 \email{523503, second\_author\}@kist.re.kr, third\_author@dc.mu.edu}
@@
 
-\abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
+% \abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
+% \abstract{
+%   Precise event spotting is crucial for sports video analysis, where understanding both the timing and location of key actions is essential, especially in fast-paced games like volleyball.
+We introduce a new task: high-precision spatial-temporal event spotting in volleyball videos, focusing on detecting both when and where key events occur.
+To address this challenge, we develop a novel volleyball dataset with annotations for temporal and spatial event localization.
+Our multi-task deep learning model jointly predicts event timing and spatial coordinates, and we find that adding a spatial predictor improves temporal detection by ???\%, highlighting the synergy between spatial and temporal tasks.
+To the best of our knowledge, this is the first work to tackle this task, setting a strong baseline for future research in spatial-temporal event spotting.
+% }
+
+% \abstract{
+%   Understanding both when and where events occur is crucial for analyzing sports videos, especially in fast-paced games like volleyball.
+We introduce a new task: high-precision spatial-temporal event spotting, targeting the challenge of localizing key events both temporally and spatially.
+To achieve this, we present a novel annotated volleyball dataset and propose a multi-task deep learning model.
+By integrating spatial predictions, our approach improves temporal event detection by 10\%, showing a strong interaction between spatial and temporal tasks.
+This is the first known work to address this task, establishing a baseline for future studies.
+% }
+
+% \abstract{
+%   Understanding the precise timing and location of events is critical for analyzing sports videos, especially in high-speed sports like volleyball.
+We introduce a new task: high-precision spatial-temporal event spotting, which focuses on detecting both the timing and location of key actions.
+To address this, we present the KOVO Event Dataset, consisting of 947 volleyball rally videos, 890,797 frames, and 5,935 key actions, annotated for both temporal and spatial localization.
+Our multi-task deep learning model jointly predicts event times and locations, and we find that incorporating spatial predictions improves temporal accuracy by 10\%.
+To the best of our knowledge, this is the first work to address this task, setting a strong baseline for future research in spatial-temporal event spotting.
+% }
+
+\abstract{
+  Understanding the precise timing and location of events is crucial for analyzing sports videos, especially in fast-paced sports like volleyball.
+We introduce a new task: high-precision spatial-temporal event spotting, which aims to detect both when and where key actions occur.
+To support this, we present the KOVO Volleyball Event Dataset, featuring 947 rally videos, 890,797 frames, and 5,935 events, annotated for both temporal and spatial localization.
+Our best model achieves a temporal mAP of 90.59, a spatial mAP of 77.94, and a combined mAP of 85.46 across various temporal and spatial thresholds.
+Notably, we find that incorporating spatial predictions enhances mAP by 10\%, underscoring the synergy between spatial and temporal analysis.
+To the best of our knowledge, this is the first work addressing this task, establishing a strong baseline for future research in spatial-temporal event spotting.
+}
 

### 2024-10-16 Paper.tex
Update Paper.tex for high-precision spatial-temporal event spotting in volleyball
- Updated the abstract to emphasize the importance of understanding the precise timing and location of events in fast-paced sports like volleyball.
- Removed outdated references to the conference proceedings and retyping requirements.
- Added a new section on related work in the field of action spotting.
- Introduced the new task of high-precision spatial-temporal event spotting in volleyball.
- Described the KOVO Event Dataset, the first dataset with detailed temporal and spatial annotations for volleyball ralli

--- 2024-10-15 Paper.tex
@@
 
-\author{\authorname{Hoang Quoc Nguyen\sup{1}\orcidAuthor{0009-0002-2004-9285}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
+\author{\authorname{Hoang Quoc Nguyen\sup{1}\sup{2}\orcidAuthor{0009-0002-2004-9285}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
 \affiliation{\sup{1}Korea Institute of Science and Technology, Seoul, Republic of Korea}
-\affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
+\affiliation{\sup{2}University of Science and Technology, Daejeon, Republic of Korea}
 \email{523503, second\_author\}@kist.re.kr, third\_author@dc.mu.edu}
@@
 
-% \abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
 \abstract{
-  Accurate event spotting in sports videos relies not only on precise temporal detection but also on spatial understanding of key actions within the frame.
-In volleyball, where fast-paced plays unfold in specific court areas, integrating spatial localization is essential for meaningful analysis.
-We introduce a new task: high-precision spatial-temporal event spotting in volleyball videos, addressing the need to detect both when and where key events occur.
-To tackle this challenge, we develop a novel volleyball event dataset annotated for both temporal and spatial event localization.
-Our proposed multi-task deep learning model leverages this dual focus, jointly predicting event timing and spatial coordinates.
-Remarkably, we find that adding a spatial predictor improves temporal event detection by ???\%, underscoring the synergy between spatial and temporal tasks.
-Evaluations demonstrate state-of-the-art performance on our dataset, surpassing existing methods in mean Average Precision (mAP), and highlighting the benefits of spatial-temporal networks in sports video analysis.
+  Understanding the precise timing and location of events is crucial for analyzing sports videos, especially in fast-paced sports like volleyball.
+We introduce a new task: high-precision spatial-temporal event spotting, which aims to detect both when and where key actions occur.
+To support this, we present the KOVO Volleyball Event Dataset, featuring 947 rally videos, and 5,935 events, annotated for both temporal and spatial localization.
+Our best model achieves a combined mAP of 85.46 across various temporal and spatial thresholds.
+Notably, we find that incorporating spatial predictions enhances temporal mAP by 5.89, underscoring the synergy between spatial and temporal analysis.
+To the best of our knowledge, this is the first work addressing this task, establishing a strong baseline for future research in spatial-temporal event spotting.
 }
@@
 \label{sec:introduction}
+% \section{Introduction}
+Video understanding has emerged as a cornerstone in computer vision, offering valuable insights into dynamic scenes for applications such as sports analytics, surveillance, and autonomous systems.
+Within this field, various tasks have been defined to interpret actions over time.
+\textit{Temporal Action Detection (TAD)} focuses on pinpointing time intervals where specific actions occur within untrimmed videos, while \textit{Temporal Action Segmentation (TAS)} aims to divide videos into continuous sequences of actions.
+Complementing these is the task of \textit{Action Spotting}, which zeroes in on identifying the precise frames that capture key events, requiring models to discern subtle temporal differences and visually similar frames \cite{spot22}.
 
-Your paper will be part of the conference proceedings
-therefore we ask that authors follow the guidelines explained in
-this example in order to achieve the highest quality possible
-\cite{Smith98}.
+Recent advancements in action spotting, such as \textit{T-DEED} \cite{teed23} and \textit{spot22} \cite{spot22}, have demonstrated the ability of models to achieve frame-level precision in fast-paced events by leveraging deep learning architectures.
+However, most of these efforts focus solely on detecting events in specific domains like figure skating and diving.
+While effective in their respective domains, they do not capture the unique challenges posed by team-based sports with rapid dynamics, such as volleyball.
 
-Be advised that papers in a technically unsuitable form will be
-returned for retyping. After returned the manuscript must be
-appropriately modified.
+Despite progress in action spotting, there is a gap in applying these techniques to sports like volleyball, where rapid play transitions occur within specific areas of the court.
+Addressing this requires a broader focus: \textit{high-precision spatial-temporal event spotting}, a task designed to detect both the exact timing and spatial location of key events.
+Unlike conventional action spotting, this task provides richer insights into player positioning and movement patterns, crucial for analyzing volleyball gameplay.
+
+In other sports, datasets like \textit{SoccerNet} have pushed the boundaries of action spotting through rich temporal and spatial annotations, significantly advancing model capabilities.
+Yet, no equivalent dataset exists for volleyball, a sport characterized by its rapid exchanges and the need for precise localization of actions.
+To fill this gap, we introduce the \textit{KOVO Event Dataset}, comprising 947 rally videos, 890,797 frames, and 5,935 annotated key actions.
+This dataset offers granular annotations for both temporal and spatial event localization, making it a valuable resource for developing models that capture the intricacies of volleyball.
+
+Our contributions are threefold.
+First, we introduce the new task of high-precision spatial-temporal event spotting, specifically tailored for the dynamics of volleyball.
+Second, we present the \textit{KOVO Event Dataset}, the first of its kind to include detailed temporal and spatial annotations for volleyball rallies.
+Third, we propose a multi-task deep learning model that jointly predicts event timing and spatial positions, leveraging this dual focus to achieve improved performance.
+Notably, incorporating spatial predictions into our model enhances temporal mAP by 5.89 points.
+Our best model achieves a temporal mAP of 90.59, a spatial mAP of 77.94, and a combined mAP of 85.46, providing a strong baseline for this new task.
+To the best of our knowledge, this work is the first to explore high-precision spatial-temporal event spotting in volleyball, setting the stage for future research in this area.
+The paper proceeds with a discussion of related work in Section 2, a detailed description of our approach in Section 3, the experimental setup in Section 4, results in Section 5, and conclusions in Section 6.
 
@@
 {\small
-\bibliography{example}}
+\bibliography{cite}}
 

### 2024-10-16 Paper.tex
Update Paper.tex for high-precision spatial-temporal event spotting in volleyball

@@
 \label{sec:introduction}
-% \section{Introduction}
 Video understanding has emerged as a cornerstone in computer vision, offering valuable insights into dynamic scenes for applications such as sports analytics, surveillance, and autonomous systems.
@@
 \textit{Temporal Action Detection (TAD)} focuses on pinpointing time intervals where specific actions occur within untrimmed videos, while \textit{Temporal Action Segmentation (TAS)} aims to divide videos into continuous sequences of actions.
-Complementing these is the task of \textit{Action Spotting}, which zeroes in on identifying the precise frames that capture key events, requiring models to discern subtle temporal differences and visually similar frames \cite{spot22}.
+Complementing these is the task of \textit{Action Spotting}, which identifies the precise frames that capture key events, requiring models to discern subtle temporal differences and visually similar frames \cite{spot22}.
 
-Recent advancements in action spotting, such as \textit{T-DEED} \cite{teed23} and \textit{spot22} \cite{spot22}, have demonstrated the ability of models to achieve frame-level precision in fast-paced events by leveraging deep learning architectures.
-However, most of these efforts focus solely on detecting events in specific domains like figure skating and diving.
-While effective in their respective domains, they do not capture the unique challenges posed by team-based sports with rapid dynamics, such as volleyball.
+Recent advancements in action spotting, such as \textit{T-DEED} \cite{tdeed23} and \textit{E2E-Spot} \cite{spot22}, have demonstrated the ability of models to achieve frame-level precision in fast-paced events using deep learning architectures.
+However, most of these efforts focus solely on detecting events in domains like figure skating and diving, without capturing the unique challenges posed by team-based sports with rapid dynamics, such as volleyball.
 
-Despite progress in action spotting, there is a gap in applying these techniques to sports like volleyball, where rapid play transitions occur within specific areas of the court.
-Addressing this requires a broader focus: \textit{high-precision spatial-temporal event spotting}, a task designed to detect both the exact timing and spatial location of key events.
+In volleyball, rapid play transitions occur within specific areas of the court, making precise spatial localization as important as temporal accuracy.
+To address this, we introduce the new task of \textit{high-precision spatial-temporal event spotting}, designed to detect both the exact timing and spatial location of key events.
 Unlike conventional action spotting, this task provides richer insights into player positioning and movement patterns, crucial for analyzing volleyball gameplay.
 
-In other sports, datasets like \textit{SoccerNet} have pushed the boundaries of action spotting through rich temporal and spatial annotations, significantly advancing model capabilities.
+In other sports, datasets like \textit{SoccerNet-v2} \cite{soccernetv2} have pushed the boundaries of action spotting through rich temporal and spatial annotations, significantly advancing model capabilities.
 Yet, no equivalent dataset exists for volleyball, a sport characterized by its rapid exchanges and the need for precise localization of actions.
@@
 To the best of our knowledge, this work is the first to explore high-precision spatial-temporal event spotting in volleyball, setting the stage for future research in this area.
-The paper proceeds with a discussion of related work in Section 2, a detailed description of our approach in Section 3, the experimental setup in Section 4, results in Section 5, and conclusions in Section 6.
+% The paper proceeds with a discussion of related work in Section 2, a detailed description of our approach in Section 3, the experimental setup in Section 4, results in Section 5, and conclusions in Section 6.
 

### 2024-10-16 Paper.tex
Update cite.bib with new references for fine-grained sports action recognition

@@
 Our best model achieves a combined mAP of 85.46 across various temporal and spatial thresholds.
-Notably, we find that incorporating spatial predictions enhances temporal mAP by 5.89, underscoring the synergy between spatial and temporal analysis.
+Notably, we find that incorporating spatial predictions enhances temporal mAP by 5.89 points, underscoring the synergy between spatial and temporal analysis.
 To the best of our knowledge, this is the first work addressing this task, establishing a strong baseline for future research in spatial-temporal event spotting.
@@
 Recent advancements in action spotting, such as \textit{T-DEED} \cite{tdeed23} and \textit{E2E-Spot} \cite{spot22}, have demonstrated the ability of models to achieve frame-level precision in fast-paced events using deep learning architectures.
-However, most of these efforts focus solely on detecting events in domains like figure skating and diving, without capturing the unique challenges posed by team-based sports with rapid dynamics, such as volleyball.
+Datasets like \textit{FigureSkating} \cite{figureskating} and \textit{FineDiving} \cite{finediving} have been pivotal in advancing action spotting, emphasizing the importance of precise temporal detection in sports with individual athletes.
+However, these datasets are tailored to specific sports and do not capture the complexity and rapid dynamics of team-based, high-speed sports, such as volleyball.
 
@@
 To the best of our knowledge, this work is the first to explore high-precision spatial-temporal event spotting in volleyball, setting the stage for future research in this area.
+
 % The paper proceeds with a discussion of related work in Section 2, a detailed description of our approach in Section 3, the experimental setup in Section 4, results in Section 5, and conclusions in Section 6.
@@
 
-We strongly encourage authors to use this document for the
-preparation of the camera-ready. Please follow the instructions
-closely in order to make the volume look as uniform as possible
-\cite{Moore99}.
+\subsection{Video Classification}
 
-Please remember that all the papers must be in English and without
-orthographic errors.
+\subsection{Temporal Action Localization}
 
-Do not add any text to the headers (do not set running heads) and
-footers, not even page numbers, because text will be added
-electronically.
+\subsection{Precise Action Spotting}
 
-For a best viewing experience the used font must be Times New
-Roman, except on special occasions, such as program code
-\ref{subsubsec:program_code}.
-
-\subsection{Manuscript Setup}
-
-The template is composed by a set of 7 files, in the
-following 2 groups:\\
-\noindent {\bf Group 1.} To format your paper you will need to copy
-into your working directory, but NOT edit, the following 4 files:
-\begin{verbatim}
-  - apalike.bst
-  - apalike.sty
-  - article.cls
-  - scitepress.sty
-\end{verbatim}
-
-\noindent {\bf Group 2.} Additionally, you may wish to copy and edit
-the following 3 example files:
-\begin{verbatim}
-  - example.bib
-  - example.tex
-  - scitepress.eps
-\end{verbatim}
-
-\subsection{Page Setup}
-
-The paper size must be set to A4 (210x297 mm). The document
-margins must be the following:
-
-\begin{itemize}
-    \item Top: 3,3 cm;
-    \item Bottom: 4,2 cm;
-    \item Left: 2,6 cm;
-    \item Right: 2,6 cm.
-\end{itemize}
-
-It is advisable to keep all the given values because any text or
-material outside the aforementioned margins will not be printed.
-
-\subsection{First Section}
-
-This section must be in one column.
-
-\subsubsection{Title and Subtitle}
-
-Use the command \textit{$\backslash$title} and follow the given structure in "example.tex". The title and subtitle must be with initial letters
-capitalized (titlecased).
-The separation between the title and subtitle is done by adding a colon ":" just before the subtitle beginning.
-In the title or subtitle, words like "is", "or", "then", etc.
-should not be capitalized unless they are the first word of the title or subtitle.
-No formulas or special characters of any form or language are allowed in the title or subtitle.
-
-\subsubsection{Authors and Affiliations}
-
-Use the command \textit{$\backslash$author} and follow the given structure in "example.tex". Please note that the name of each author must start with its first name.
-
-\subsubsection{Keywords}
-
-Use the command \textit{$\backslash$keywords} and follow the given structure in "example.tex".
-Each paper must have at least one keyword.
-If more than one is specified, please use a comma as a separator.
-The sentence must end with a period.
-
-\subsubsection{Abstract}
-
-Use the command \textit{$\backslash$abstract} and follow the given structure in "example.tex".
-Each paper must have an abstract up to 200 words. The sentence
-must end with a period.
-
-\subsection{Second Section}
-
-Files "example.tex" and "example.bib" show how to create a paper
-with a corresponding list of references.
-
-This section must be in two columns.
-
-Each column must be 7,5-centimeter wide with a column spacing
-of 0,8-centimeter.
-
-The section text must be set to 10-point.
-
-Section, subsection and sub-subsection first paragraph should not
-have the first line indent.
-
-To remove the paragraph indentation (only necessary for the
-sections), use the command \textit{$\backslash$noindent} before the
-paragraph first word.
-
-If you use other style files (.sty) you MUST include them in the
-final manuscript zip file.
-
-\subsubsection{Section Titles}
-
-The heading of a section title should be in all-capitals.
-
-Example: \textit{$\backslash$section\{FIRST TITLE\}}
-
-\subsubsection{Subsection Titles}
-
-The heading of a subsection title must be with initial letters
-capitalized (titlecased).
-
-Words like "is", "or", "then", etc. should not be capitalized unless
-they are the first word of the subsection title.
-
-Example: \textit{$\backslash$subsection\{First Subtitle\}}
-
-\subsubsection{Sub-Subsection Titles}
-
-The heading of a sub subsection title should be with initial letters
-capitalized (titlecased).
-
-Words like "is", "or", "then", etc should not be capitalized unless
-they are the first word of the sub subsection title.
-
-Example: \textit{$\backslash$subsubsection\{First Subsubtitle\}}
-
-\subsubsection{Tables}
-
-Tables must appear inside the designated margins or they may span
-the two columns.
-
-Tables in two columns must be positioned at the top or bottom of the
-page within the given margins. To span a table in two columns please add an asterisk (*) to the table \textit{begin} and \textit{end} command.
-
-Example: \textit{$\backslash$begin\{table*\}}
-
-\hspace*{1.5cm}\textit{$\backslash$end\{table*\}}\\
-
-Tables should be centered and should always have a caption
-positioned above it. The font size to use is 9-point. No bold or
-italic font style should be used.
-
-The final sentence of a caption should end with a period.
-
-\begin{table}[h]
-\caption{This caption has one line so it is
-centered.}\label{tab:example1} \centering
-\begin{tabular}{|c|c|}
-  \hline
-  Example column 1 & Example column 2 \\
-  \hline
-  Example text 1 & Example text 2 \\
-  \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[h]
-\vspace{-0.2cm}
-\caption{This caption has more than one line so it has to be
-justified.}\label{tab:example2} \centering
-\begin{tabular}{|c|c|}
-  \hline
-  Example column 1 & Example column 2 \\
-  \hline
-  Example text 1 & Example text 2 \\
-  \hline
-\end{tabular}
-\end{table}
-
-Please note that the word "Table" is spelled out.
-
-\subsubsection{Figures}
-
-Please produce your figures electronically, and integrate them into
-your document and zip file.
-
-Check that in line drawings, lines are not interrupted and have a
-constant width. Grids and details within the figures must be clearly
-readable and may not be written one on top of the other.
-
-Figure resolution should be at least 300 dpi.
-
-Figures must appear inside the designated margins or they may span
-the two columns.
-
-Figures in two columns must be positioned at the top or bottom of
-the page within the given margins. To span a figure in two columns please add an asterisk (*) to the figure \textit{begin} and \textit{end} command.
-
-Example: \textit{$\backslash$begin\{figure*\}}
-
-\hspace*{1.5cm}\textit{$\backslash$end\{figure*\}}
-
-Figures should be centered and should always have a caption
-positioned under it. The font size to use is 9-point. No bold or
-italic font style should be used.
-
-\begin{figure}[!h]
-  \centering
-   {\epsfig{file = SCITEPRESS.eps, width = 5.5cm}}
-  \caption{This caption has one line so it is centered.}
-  \label{fig:example1}
- \end{figure}
-
-\begin{figure}[!h]
-  \vspace{-0.2cm}
-  \centering
-   {\epsfig{file = SCITEPRESS.eps, width = 5.5cm}}
-  \caption{This caption has more than one line so it has to be justified.}
-  \label{fig:example2}
-\end{figure}
-
-The final sentence of a caption should end with a period.
-
-Please note that the word "Figure" is spelled out.
-
-\subsubsection{Equations}
-
-Equations should be placed on a separate line, numbered and
-centered.\\The numbers accorded to equations should appear in
-consecutive order inside each section or within the contribution,
-with the number enclosed in brackets and justified to the right,
-starting with the number 1.
-
-Example:
-
-\begin{equation}\label{eq1}
-    a=b+c
-\end{equation}
-
-\subsubsection{Algorithms and Listings}
-
-Algorithms and Listings captions should have font size 9-point, no bold or
-italic font style should be used and the final sentence of a caption should end with a period.
-The separator between the title of algorithms/listings and the name of the algorithm/listing must be a colon.
-Captions with one line should be centered and if it has more than one line it should be set to justified.
-
-\begin{algorithm}[!h]
- \caption{How to write algorithms.}
- \KwData{this text}
- \KwResult{how to write algorithm with \LaTeX2e }
- initialization\;
- \While{not at end of this document}{
-  read current\;
-  \eIf{understand}{
-   go to next section\;
-   current section becomes this one\;
-   }{
-   go back to the beginning of current section\;
-  }
- }
-\end{algorithm}
-
-\bigskip
-\subsubsection{Program Code}\label{subsubsec:program_code}
-
-Program listing or program commands in text should be set in
-typewriter form such as Courier New.
-
-Example of a Computer Program in Pascal:
-
-\begin{small}
-\begin{verbatim}
- Begin
-     Writeln('Hello World!!');
- End.
-\end{verbatim}
-\end{small}
-
-The text must be aligned to the left and in 9-point type.
-
-\subsubsection{Reference Text and Citations}
-
-References and citations should follow the APA (Author, date)
-System Convention (see the References section in the compiled
-manuscript). As example you may consider the citation
-\cite{Smith98}. Besides that, all references should be cited in the
-text. No numbers with or without brackets should be used to list the
-references.
-
-References should be set to 9-point. Citations should be 10-point
-font size.
-
-You may check the structure of "example.bib" before constructing the
-references.
-
-For more instructions about the references and citations usage
-please see the appropriate link at the conference website.
+\section{\uppercase{DATASET OVERVIEW}}
+\subsection{Data Content and Statistics}
+\subsection{Annotation Process}
+\subsection{Dataset Splits}
+\subsection{Evaluation Metrics}
 
 \section{\uppercase{PROPOSED METHOD}}
-
-For the mutual benefit and protection of Authors and
-Publishers, it is necessary that Authors provide formal written
-Consent to Publish and Transfer of Copyright before publication of
-the Book. The signed Consent ensures that the publisher has the
-Author's authorization to publish the Contribution.
-
-The copyright form is located on the authors' reserved area.
-
-The form should be completed and signed by one author on
-behalf of all the other authors.
+\subsection{Problem Formulation}
+\subsection{Model Architecture}
+\subsubsection{Feature Extractor}
+\subsubsection{Temporal Event Detection}
+\subsubsection{Spatial Event Detection}
+\subsubsection{Multi-Task Learning}
+\subsubsection{Loss Function}
 

### 2024-10-16 Paper.tex
Update Paper.tex for high-precision spatial-temporal event spotting in volleyball

@@
 
+% TODO: Fill this when finish paper
 % The paper proceeds with a discussion of related work in Section 2, a detailed description of our approach in Section 3, the experimental setup in Section 4, results in Section 5, and conclusions in Section 6.
@@
 \subsection{Video Classification}
+In video understanding, video classification focuses on predicting a single label for the entire video, unlike event spotting, which demands precise frame-level labeling.
+This difference leads to distinct challenges: video classification often benefits from sparse frame sampling \cite{tsn}, while event spotting requires dense sampling to capture rapid changes in events.
+Additionally, classification models frequently use techniques like global space-time pooling \cite{8578773} or temporal consensus \cite{zhou2018temporalrelationalreasoningvideos} to derive a video-level prediction, which contrasts with the need for maintaining high temporal resolution in event spotting.
 
-\subsection{Temporal Action Localization}
+Drawing from insights provided by E2E-Spot, which demonstrated the advantages of end-to-end training without temporal pooling for frame-level precision, our approach adopts RegNet-Y \cite{radosavovic2020designingnetworkdesignspaces} combined with GSM \cite{9156729}.
+RegNet-Y, known for its efficient architecture, paired with GSM for adaptive temporal shifts, offers a robust solution for extracting spatial-temporal features.
+This combination proved particularly effective for our high-precision event spotting task in volleyball, enabling both temporal accuracy and spatial precision while keeping the process efficient.
+
+\subsection{Group Activity Recognition}
 

### 2024-10-16 Paper.tex
Refactor Paper.tex for better organization and clarity
Update cite.bib with new references for fine-grained sports action recognition

--- 2024-10-16 Paper.tex
@@
 Video understanding has emerged as a cornerstone in computer vision, offering valuable insights into dynamic scenes for applications such as sports analytics, surveillance, and autonomous systems.
-Within this field, various tasks have been defined to interpret actions over time.
-\textit{Temporal Action Detection (TAD)} focuses on pinpointing time intervals where specific actions occur within untrimmed videos, while \textit{Temporal Action Segmentation (TAS)} aims to divide videos into continuous sequences of actions.
-Complementing these is the task of \textit{Action Spotting}, which identifies the precise frames that capture key events, requiring models to discern subtle temporal differences and visually similar frames \cite{spot22}.
+This field encompasses various tasks designed to interpret and analyze actions over time.
+Among these, \textit{Video Classification} aims to assign a single label to an entire video, providing a broad understanding of the content but often lacking frame-level precision.
+In contrast, \textit{Temporal Action Localization (TAL)} focuses on identifying time intervals where specific actions occur within untrimmed videos.
+Complementing these is \textit{Precise Action Spotting (PES)}, which identifies the precise frames that capture key events, requiring models to discern subtle temporal differences and distinguish visually similar frames \cite{spot22}.
 
@@
 To address this, we introduce the new task of \textit{high-precision spatial-temporal event spotting}, designed to detect both the exact timing and spatial location of key events.
-Unlike conventional action spotting, this task provides richer insights into player positioning and movement patterns, crucial for analyzing volleyball gameplay.
+Unlike conventional action spotting, this task provides richer insights into player positioning and movement patterns, which are crucial for analyzing volleyball gameplay.
 
@@
 
-Our contributions are threefold.
-First, we introduce the new task of high-precision spatial-temporal event spotting, specifically tailored for the dynamics of volleyball.
-Second, we present the \textit{KOVO Event Dataset}, the first of its kind to include detailed temporal and spatial annotations for volleyball rallies.
-Third, we propose a multi-task deep learning model that jointly predicts event timing and spatial positions, leveraging this dual focus to achieve improved performance.
+Our contributions are threefold:
+\begin{itemize}
+    \item \textbf{New Task Introduction:} We introduce the task of high-precision spatial-temporal event spotting, specifically tailored for the dynamics of volleyball.
+    \item \textbf{Dataset Development:} We present the \textit{KOVO Event Dataset}, the first of its kind to include detailed temporal and spatial annotations for volleyball rallies, aimed at fostering research in this area.
+    \item \textbf{Model Development:} We propose a multi-task deep learning model that jointly predicts event timing and spatial positions, leveraging this dual focus to achieve improved performance.
 Notably, incorporating spatial predictions into our model enhances temporal mAP by 5.89 points.
+\end{itemize}
+
 Our best model achieves a temporal mAP of 90.59, a spatial mAP of 77.94, and a combined mAP of 85.46, providing a strong baseline for this new task.
@@
 \subsection{Video Classification}
+Video classification aims to predict a single label for an entire video, in contrast to event spotting, which requires precise frame-level labeling.
+This distinction introduces unique challenges: video classification can leverage sparse frame sampling \cite{tsn}, whereas event spotting demands dense sampling to capture rapid changes in events.
+Additionally, classification models often employ global space-time pooling \cite{8578773} or temporal consensus \cite{zhou2018temporalrelationalreasoningvideos} to produce video-level predictions, while event spotting necessitates preserving high temporal resolution.
+
+Building on insights from E2E-Spot, which highlighted the benefits of end-to-end training without temporal pooling for frame-level precision, our method employs RegNet-Y \cite{radosavovic2020designingnetworkdesignspaces} with GSM \cite{9156729}.
+RegNet-Y, valued for its efficiency, combined with GSM’s adaptive temporal shifts, offers a powerful approach for spatial-temporal feature extraction.
+This setup is particularly suited for our high-precision event spotting task in volleyball, achieving both temporal accuracy and spatial precision efficiently.
 
 \subsection{Temporal Action Localization}
+Temporal Action Localization (TAL) aims to identify the time intervals when specific actions occur in untrimmed videos, making it ideal for longer actions that are not instantaneous.
+Unlike video classification, which assigns a single label to an entire video, TAL requires precise start and end times, making it more complex.
+
+TAL methods are typically categorized into two groups: two-stage \cite{9578330,10.1007/978-3-319-46487-9_47} and one-stage \cite{10203543,zhang2022actionformer} approaches.
+Two-stage models generate action proposals before classifying them, while one-stage models directly predict actions and their intervals in a streamlined process.
+Recent methods, like ActionFormer \cite{zhang2022actionformer} and TriDet \cite{tridet}, leverage advanced architectures, including transformers and feature pyramids, to improve temporal precision across varying action durations.
+Anchor-free approaches \cite{9171561} have further enhanced flexibility in predicting actions without relying on predefined time windows.
+
+TAL's development has been driven by extensive datasets and benchmarks such as ActivityNet \cite{ActivityNet}, EPIC-KITCHENS \cite{damen2018scalingegocentricvisionepickitchens}, and THUMOS Challenge \cite{Idrees_2017}, making it a well-explored field for understanding complex, prolonged actions in videos.
+However, it remains distinct from action spotting, which focuses on identifying brief, precise moments in fast-paced scenarios.
 
@@
 \subsection{Dataset Splits}
-\subsection{Evaluation Metrics}
+\subsection{Release and Access}
+Due to the large size of the dataset, we are unable to release the full-resolution (1280x720) videos in this paper.
+However, we have made a resized version (512x288 resolution) along with the corresponding annotations available on Kaggle, totaling 100GB.
+The dataset can be accessed at [provide link].
 
@@
 \label{sec:experiments}
-
-Please note that ONLY the files required to compile your paper should be submitted. Previous versions or examples MUST be removed from the compilation directory before submission.
-
-We hope you find the information in this template useful in the preparation of your submission.
+\subsection{Implementation Details}
+\subsection{Training Strategy}
+\subsection{Evaluation Metrics}
 

### 2024-10-16 Paper.tex
Refactor Paper.tex for better organization and clarity

@@
 
-\keywords{Temporally Precise Spotting, Video Understanding, Spatial Temporal Event Spotting, Volleyball, Sport, Deep Learning}
+\keywords{Precise Event Spotting, Video Understanding, Spatial Temporal Event Spotting, Deep Learning, Volleyball, Sport}
 
@@
 
-Building on insights from E2E-Spot, which highlighted the benefits of end-to-end training without temporal pooling for frame-level precision, our method employs RegNet-Y \cite{radosavovic2020designingnetworkdesignspaces} with GSM \cite{9156729}.
-RegNet-Y, valued for its efficiency, combined with GSM’s adaptive temporal shifts, offers a powerful approach for spatial-temporal feature extraction.
-This setup is particularly suited for our high-precision event spotting task in volleyball, achieving both temporal accuracy and spatial precision efficiently.
-
 \subsection{Temporal Action Localization}
@@
 However, it remains distinct from action spotting, which focuses on identifying brief, precise moments in fast-paced scenarios.
+\subsection{Precise Event Spotting (PES)}
 
-\subsection{Precise Action Spotting}
+Precise Event Spotting (PES) aims to detect the exact frames of key events in untrimmed videos, making it ideal for fast, critical moments in sports.
+Unlike Temporal Action Localization (TAL), which spans broader time intervals, PES requires frame-level accuracy, crucial for detailed sports analysis where slight timing shifts can alter game interpretations.
+
+Datasets like \textit{FigureSkating} \cite{figureskating} and \textit{FineDiving} \cite{finediving} have advanced PES with frame-level annotations, but focus on simpler, individual sports.
+Recent methods, such as \textit{T-DEED} \cite{tdeed23} and \textit{E2E-Spot} \cite{spot22}, enhance precision by refining temporal representations and avoiding pooling, but lack spatial context needed for team sports.
+
+In volleyball, spatial localization is as critical as timing.
+Understanding event locations is key to analyzing player movements and strategies.
+Our work addresses this by introducing a new task and dataset for high-precision spatial-temporal event spotting in volleyball, capturing both event timing and location.
+
+Inspired by \textit{E2E-Spot} \cite{spot22}, our approach uses RegNet-Y \cite{radosavovic2020designingnetworkdesignspaces} with GSM \cite{9156729} for adaptive temporal shifts.
+This combination balances efficiency and precision, making it ideal for capturing complex spatial-temporal dynamics in volleyball.
 

### 2024-10-16 Paper.tex
Refactor Paper.tex for better organization and clarity

@@
+% TODO:
+%   [ ] Write Method
+%   [ ] Write Experiments
+%   [ ] Create Diagrams
+    %   [ ] Model Architecture
+
 \documentclass[a4paper,twoside]{article}
@@
 \subsection{Problem Formulation}
+\textbf{Temporal Spatial Event Spotting (TSES)} aims to identify both the precise time and location of events within untrimmed videos.
+Given a video with \(N\) frames \(x_1, \ldots, x_N\) and a set of \(K\) event classes \(c_1, \ldots, c_K\), the goal is to predict a sparse set of frame indices where events occur, as well as the corresponding event class and spatial coordinates.
+Each prediction is represented as \((t, c_t, s_t)\), where \(t\) is the frame index, \(c_t\) is the predicted event class, and \(s_t\) is the spatial location of the event within that frame.
+A temporal prediction is considered correct if it falls within a small temporal tolerance \(\sigma_f\) frames of the labeled event and matches the ground-truth class.
+Similarly, spatial predictions are deemed correct if the distance between the predicted location \(s_t\) and the ground-truth event location is within a specified threshold \(\sigma_p\).
+For TSES, these tolerances are kept small, requiring precise frame-level accuracy, and it assumes that videos are captured with sufficiently high frame rates.
+
+To perform well on this task, several key requirements must be met:
+\begin{itemize}
+    \item \textbf{Local Spatial-Temporal Features}: The model should capture subtle visual changes and movements across neighboring frames, essential for distinguishing between similar-looking moments.
+    \item \textbf{Long-Term Temporal Context}: A broader temporal window allows the model to understand events in context, such as how player positions or actions evolve before and after a critical moment.
+    \item \textbf{Dense Per-Frame Predictions}: For each frame \(x_t\), the model produces a prediction \((\hat{y}_t, \hat{s}_t)\), where \(\hat{y}_t \in \mathbb{R}^K\) is a one-hot vector representing the predicted event class probabilities, and \(\hat{s}_t \in \mathbb{R}^2\) represents the \(x, y\) coordinates of the event within the frame.
+This ensures frame-level precision for each event.
+\end{itemize}
+
+These requirements call for a robust and end-to-end trainable architecture capable of leveraging both temporal and spatial information.
+Our approach utilizes a sequence model that integrates local spatial-temporal features.
+
 \subsection{Model Architecture}

### 2024-10-16 Paper.tex
Refactor Paper.tex for better organization and clarity

@@
 \subsection{Problem Formulation}
-\textbf{Temporal Spatial Event Spotting (TSES)} aims to identify both the precise time and location of events within untrimmed videos.
+\textbf{Spatial-Temporal Event Spotting (STES)} aims to identify both the precise time and location of events within untrimmed videos.
 Given a video with \(N\) frames \(x_1, \ldots, x_N\) and a set of \(K\) event classes \(c_1, \ldots, c_K\), the goal is to predict a sparse set of frame indices where events occur, as well as the corresponding event class and spatial coordinates.
@@
 Similarly, spatial predictions are deemed correct if the distance between the predicted location \(s_t\) and the ground-truth event location is within a specified threshold \(\sigma_p\).
-For TSES, these tolerances are kept small, requiring precise frame-level accuracy, and it assumes that videos are captured with sufficiently high frame rates.
+For STES, these tolerances are kept small, requiring precise frame-level accuracy, and it assumes that videos are captured with sufficiently high frame rates.
 
@@
     \item \textbf{Long-Term Temporal Context}: A broader temporal window allows the model to understand events in context, such as how player positions or actions evolve before and after a critical moment.
-    \item \textbf{Dense Per-Frame Predictions}: For each frame \(x_t\), the model produces a prediction \((\hat{y}_t, \hat{s}_t)\), where \(\hat{y}_t \in \mathbb{R}^K\) is a one-hot vector representing the predicted event class probabilities, and \(\hat{s}_t \in \mathbb{R}^2\) represents the \(x, y\) coordinates of the event within the frame.
-This ensures frame-level precision for each event.
+    \item \textbf{Dense Per-Frame Predictions}: For each frame \(x_t\), the model produces a prediction \((\hat{y}_t, \hat{s}_t)\), where \(\hat{y}_t \in \mathbb{R}^K\) is a vector of logits representing class probabilities, and \(\hat{s}_t \in \mathbb{R}^2\) represents the \(x, y\) coordinates of the event within the frame.
+The final class \(c_t\) is obtained by applying argmax to \(\hat{y}_t\), ensuring frame-level precision for each event.
 \end{itemize}
